Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2020-12-07 manuscript/draft_rsfmri.Rmd

Whole brain FC maps will be calculated using Pearson’s correlation between average seed time series and whole brain timeseries on the subject level (using nilearn). After transforming from r-to-Z, we will transform the images into Freesurfer longitudinal space, using /mri/transforms/_to_.lta). Then, will calculate difference maps between BL-FU1 (confirmatory hypothesis), BL-FU2, FU1-FU2 (exploratory hypotheses). These images will be transformed into MNI space (using ANTS non-linear registration from the longitudinal template to MNI space) for statistical analysis.
Aggregated FC values will be calculated using Pearson’s correlation of average seed time series from pre-defined in the longitudinal template space. Aggregated values will be extracted for the reward and the default mode network.

>>>>

Quality control:
- Freesurfer segmentations and surfaces will be visually controlled and corrected according to published recommendations, if necessary.
- Participants who cannot be correctly preprocessed due to (uncorrectable) artifacts in the T1-weighted or resting-state fMRI will be excluded.
-  We will first perfom the analysis with all participants who were correctly preprocessed. In a sensitivity analysis, participants with mean FD larger than the average mean FD + 2 standard deviations will be excluded.
